Ecology and Conservation Modelling Preregistration Template -- DRAFT

### 2020-06-01 analysis/preregistration_template.Rmd
Update analysis/preregistration_template.Rmd
move in-text comment to GH comment

*Collect, process and prepare data available for parameterisation, determining model structure, and for scenario analysis.*
HF - this isn't super clear to me. Maybe we need more clarification here or an example

>>>>

*Collect, process and prepare data available for parameterisation, determining model structure, and for scenario analysis.*
